Draft

### 2017-08-31 Thesis/Draft.tex
Add D-Tracking Rule

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\section{\texorpdfstring{Thresholding Bandit Problem
\label{chap:ThresholdingBanditProblem}}{Thresholding Bandit Problem }}\label{thresholding-bandit-problem}

@@

\subsection{\texorpdfstring{Lower Bound: Theorem and Proof
\label{sec:LowerBoundLocatelli}}{Lower Bound: Theorem and Proof }}\label{lower-bound-theorem-and-proof}

@@

\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
\ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower
bound for the thresholding bandit problem is shown. The basic idea is as
follows. The problem formulation considered in the paper describes
bandit problems for sub-Gaussian distributions. To show a lower bound,
we show that every algorithm is expected to make a certain error even if
we restrict ourselves to a very restricted scenario. Even then, any
algorithm will have a certain level of risk with which it cannot
distinguish between the actual setting and slightly changed settings
(under which the former answer leads to regret).

To be more specific, consider a case in which we set \(\tau = 0\) and
\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
distributed feedback with means \(\mu_i\), we see that for each arm
\(i\) the distance from the threshold is given by
\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
variance of 1 for every arm, we have for every arm the distribution
\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
define for each arm \(i \in \{1, \dots, K\}\) the alternative
distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
that in this case, this is equivalent to a ``flip around the
threshold''. Arms that originally have a mean larger than the threshold
have a mean smaller than the threshold after the flip.

The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
sample for every time point \(t\in \{1, \dots, T\}\) from its
distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
we have a \(T \times K\) table of realized observations from the product
distribution given by
\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
This is a product distribution where the \(K\) different means all lie
above the threshold. We would hope that an algorithm classifies the
means accordingly. However, we will show in what follows that any
algorithm makes a certain error by not being able to distinguish
\(\mathcal{B}^0\) from at least one of \(K\) alternative product
distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
differs only slightly in one arm from the original distribution, and has
the same overall complexity (as defined by
\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
distributions so that an arm sampling arm \(i\) very often for some
reason will not have a smaller lower bound by chance.

For each of the \(K\) arms, we introduce an alternative model of the
following kind. Before the start of the algorithm, we introduce a slight
variation in the setup. The idea is similar to how one can switch arms
in the pure exploration setup for multi-armed bandits (compare Audibert
et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
without introducing additional complexity to the specified problem.
However, since we do not compare arms directly with each other in the
thresholding bandit problem (switching arms would still keep all means
above the threshold), we instead need to flip an arm \(i\) with respect
to the threshold in order to get the alternative model
\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
flipped arm the new distribution \(\nu_i'\) as defined above. Indeed, we
can define the new product distribution
\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
This flipping of the arm corresponds to multiplying all random variables
\(X_{i,t}\) of arm \(i\) by \(-1\).

As in Locatelli et al. (2016), we let for \(i \leq K\),
\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
describing all samples that a bandit strategy can potentially collect up
to horizon \(T\), i.e.~according to the samples
\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
until time \(T\).

\subsubsection{Reminder about the goal of the
proof}\label{reminder-about-the-goal-of-the-proof}

At this point, we have defined a finite set of problems of Gaussian
distributions with fixed variance 1 for a given set of set of gaps
between the means of the distributions and the threshold, \((d_k)_k\).
We will now proof a lower bound on the worst case regret of any
algorithm; that is, the maximum error probability that even the best
algorithm makes on this problem.

Given our formulation of the regret, the expected regret
\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
of making a wrong classification of any of the \(K\) means. In general,
let \(g\) be a binary decision function, and define
\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
decision \(T\) distinguishes between two states of the world, \(H_0\)
and \(H_1\). Then our overall error probability is given by
\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).

In our case, \(H_0\) may correspond to the state in which we have
\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
which the algorithm, making the decision, classifies arm \(i\) as being
above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The
event on which all arms are being classified as above the threshold is
consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
Theorem 1 does not bound the overall regret, but the maximum error
probability on the \(K+1\) different models. We can write this now as

In order to give a bound on above equation, we start by considering
\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
written as the expected change in the likelihood of observed data when
moving from distribution \(P_{\mathcal{B}_0}\) to \(P_{\mathcal{B}_i}\),
times the probability under the original state. In other words, the
probability of event \(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is
given as the probability of \(\mathcal{A}_i\) under the (original) state
\(\mathcal{B}^0\) multiplied by a factor. This factor describes whether
the new distribution increases or decreases the probability of the
event, and is given by the change in the data likelihoods due to moving
from \(\mathcal{B}^0\) to \(\mathcal{B}^i\), expressed as the expected
likelihood ratio under \(\mathcal{B}^0\). By definition, the latter is
equal to the empirical Kullback-Leibler divergence of the two
distributions.

We will define the change of distribution in terms of the empirical
log-likelihood for our case. Then, we will show how to replace the
log-likelihood by the empirical Kullback-Leibler divergence. So let us
first introduce the empirical Kullback-Leibler divergence.

Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
\(\lambda\). Then their density functions are given by
\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
\end{align*}

Since we consider Gaussian distributions with variance 1, we have
density functions
\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
this into the above definition of the empirical Kullback-Leibler
divergence, we easily see

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
\end{align*}

We are now ready to state the change of distribution. As alluded to
above, we consider how the probability changes for the event
\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
\(\mathcal{B}^i\). When flipping arm \(i\), we only changed the samples
of this arm, that is, the first \(T_i\) observations we got from arm
\(i\) the algorithm took. The change of distribution is then defined as:

For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).

It is easy to see that

Part of our bound is
\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
so let's continue with that. In general it holds that
\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
Thus we can write:

where the second line is again the intersection of \(\mathcal{A}_i\) and
\(\xi\) as before in order to apply the change of distribution in the
third line.

What is left to show before we have our final bound is a bound on
\(T_i\). To show that any algorithm has a certain bound on its error, it
only makes sense that every arm has to pulled at least a certain amount
of times. Consequently, no arm should be pulled exclusively.

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
\end{align*}

Furthermore, we know that the sum of the individual arm pulls has to be
equal to the overall number of pulls (equal to the budget in the fixed
budget sense), \(\sum_i T_i = T\), and furthermore we know that
\(T_i>0\). The latter holds since any reasonable algorithm has to check
each arm at least once in our setup. This is because we need to check
each arm's performance in comparison to the threshold. Thus it is easy
to show that
\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
To see this, assume the opposite:
\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
implies however
\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
which is a contradiction.

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
\end{align*}

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

Consider again the risk which we need to bound from equation
\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
over all \(\mathcal{B}_i\). By again using the fact that in general
\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
we plug in our previous calculations:

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
\end{align}

@@

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and Top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.

@@

\section{\texorpdfstring{Kullback-Leibler Complexity of Pure Exploration
\label{chap:KullbackLeiblerPureExploration}}{Kullback-Leibler Complexity of Pure Exploration }}\label{kullback-leibler-complexity-of-pure-exploration}

In the previous chapter, we discussed the thresholding bandit problem as
presented in Locatelli et al. (2016). Doing so, we came across the
complexity term \(H = \sum_{i=1}^{K} \Delta_i^{-2}\). Furthermore, we
noted the fact that an algorithm and bounds based on \emph{only} the gap
between the respective mean and the threshold are useful in the case of
sub-Gaussian problems. Furthermore, even for the case of Bernoulli arms,
which are sub-Gaussian since their feedback is bounded on \([0,1]\), the
gap \(\Delta\) becomes less and less appropriate in situations in which
both \(\mu\) of the Bernoulli, and \(\tau\) are very close to 0 or 1.

Even though the complexity \(H\) enjoys popularity in the literature of
the best \(m\) arm identification problem, \(m \geq 1\), Kaufmann et al.
(2016) show explicitly that \(H\) is mainly useful for problems of
Gaussian distributions. Indeed, they go so far as to define new measures
of complexity that are based on information theoretic measures. Using
these, they then frame \(H\) as an approximation to their measures in
the case of Gaussian distributions. This underlines the fact that
Bernoulli distributions with small means have to be treated differently
than Gaussian distributions.

For the current chapter, we adopt the notation of Kaufmann et al. (2016)
to ease a comparison with their arguments.

\subsection{\texorpdfstring{Complexity of Best-Arm and Top-\emph{m}
Identification}{Complexity of Best-Arm and Top-m Identification}}\label{complexity-of-best-arm-and-top-m-identification}

Instead of the thresholding bandit problem, we now consider the problem
of identifying the best \(m\) out of \(K\) arms, that is, the Top-\(m\)
problem. While we previously looked at a fixed budget formulation, we
now mainly focus on a fixed confidence problem: We hold the confidence
\(1-\delta\) fixed at which a strategy returns the correct \(m\) arms
while trying to reach this confidence in a way that minimizes the sample
complexity \(\mathbb{E}_{\nu}[\tau]\), that is, the expected number of
overall draws of the arms. \(\tau\) is also called the stopping time of
the algorithm. The goal of algorithms is to identify
\(\mathcal{S}_m^*\), the set of the \(m\) arms with the largest means.
If we let \((\mu_1, \dots, \mu_K)\) be the vector of the means of the
arms, then let \((\mu_{[1]}, \dots, \mu_{[K]})\) be the tuple in which
the means are arranged in decreasing order. For the rest of this
chapter, we consider only settings with arms for which
\(\mu_{[m]} > \mu_{[m+1]}\); we demand the set of the top \(m\) arms,
\(\mathcal{S}_m^*\), to be unique. After the sampling phase, we require
any algorithm to return the set \(\hat{S}_m \subset \{1,\dots,K\}\) of
\(m\) arms that the algorithm believes to have the largest means. In the
case of fixed confidence, we fix \(\delta\) at the beginning, such that
the algorithm only stops sampling when
\(\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta\). We try
to find algorithms who fulfill this condition as quickly as possible.
Algorithms which minimize the expected stopping time (or number of
draws), \(\mathbb{E}_{\nu}[\tau]\).

To arrive at the new measure of complexity proposed by Kaufmann et al.
(2016), it will actually make sense to first follow their arguments to a
general lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\)
in the case of fixed confidence problems. This bound is given in their
Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).

@@

Given that we are again in the Top-\(m\) setting, the proof idea is
similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
that we again consider problems where we switch arms around the limit
seperating the two groups of arms as given implicitly by \(\mu_{[m]}\)
and \(\mu_{[m+1]}\). The hope here being that these methods could be
applied to the thresholding bandit problem where the threshold of course
gives the limit between the arms above and below the threshold. As we
have seen in chapter 1, this flip around the threshold was of course
used in the proof of the lower bound in Theorem 1 of Locatelli et al.
(2016). However, there, again, the distributions were assumed to be
Gaussian. This brings the big advantage that the Kullback-Leibler
divergence becomes symmetric, and the feedback can take values on all
\(\mathbb{R}\). And by using the complexity measure \(H(\nu)\), it is
also clear that there exists an arm that is undersampled with respect to
its contribution to the overall complexity of the problem (or sampled
exactly according to its contribution), which leads to leads to a
convenient upper bound on this arms number of draws which is again
employed in both the proof of Theorem
\ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It
is not clear yet, whether the same can also be done with other
complexity measures.

@@

\subsubsection{Likelihood Ratio for Univariate Exponential Family of
Distributions}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1} \end{center}

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\section{\texorpdfstring{The Thresholding Bandit Problem
\label{chap:ThresholdingBanditProblem}}{The Thresholding Bandit Problem }}\label{the-thresholding-bandit-problem}

@@

\subsection{\texorpdfstring{Lower Bound for the Thresholding Bandit
Problem
\label{sec:LowerBoundLocatelli}}{Lower Bound for the Thresholding Bandit Problem }}\label{lower-bound-for-the-thresholding-bandit-problem}

Locatelli et al. (2016) also provide a general lower bound on the
probability of error in the thresholding bandit problem. The bound is
derived for a specified set of problems through a change in distribution
as common in the multi-armed bandit literature (compare for example
Audibert et al., 2010, or Kaufmann et al., 2016). For any of these
problems, the largest probability of error that the best algorithm
incurs is still lower bounded by the bound given below.

@@

A proof of the lower bound is given in the Appendix in
\autoref{sec:AppendixAPTLB}.

If we write the lower bound as
\(LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)\)
and the upper bound as
\(UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)\),
we see that \(LB\) and \(UB\) match up to multiplicative constants and
the \((\log(T)+1)K\) term which is negligiable in comparison with the
exponent for large \(T\) as shown in Locatelli et al. (2016), which
makes the APT algorithm order optimal.

@@

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and Top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.

@@

\section{\texorpdfstring{Information Theoretic Complexity of Pure
Exploration Bandits
\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Complexity of Pure Exploration Bandits }}\label{information-theoretic-complexity-of-pure-exploration-bandits}

The previous chapter introduces the thresholding bandit problem as
described in Locatelli et al. (2016), and with the APT strategy a first
algorithm that is simple, yet order-optimal for large budgets. However,
we end with the conclusion that a distance measure between the
distributions and the threshold based on the Kullback-Leibler divergence
might be more useful than the simple gap
\(\Delta^2_i = (\mu_i - \tau_i)^2\) employed so far. Indeed, citing
Kaufmann et al. (2016), we note that the complexity \(H\) used so far
can be considered a sub-Gaussian approximation of a better complexity
measure based on information theoretic measures like the
Kullback-Leibler divergence.

In order to give more intuition to why that is the case, and in what
ways information theoretic measures can be introduced to measure the
complexity of bandit problems, we now turn to Kaufmann et al. (2016) and
Garivier and Kaufmann (2016). The latter describes a strategy based on
Kullback-Leibler divergences for the best-arm identification problem,
while the first derives complexity measures based on the divergence.
Ideally, their work offers methods that can inform our work of extending
the thresholding bandit problem. In what follows, we adopt the notation
of Kaufmann et al. (2016) to ease a comparison with their arguments.

\subsection{\texorpdfstring{Complexity Measures for Best-Arm and
Top-\emph{m} Identification
\label{sec:KaufmannEtAl2016}}{Complexity Measures for Best-Arm and Top-m Identification }}\label{complexity-measures-for-best-arm-and-top-m-identification}

Instead of the thresholding bandit problem, Kaufmann et al. (2016)
consider the problem of identifying the best \(m\) out of \(K\) arms,
that is, the Top-\(m\) problem. They describe their a bandit model
\(\nu\) also by \(K\) arms characterized by probability distributions
\(\nu_a\), \(a \in \{1,...,K\}\) with mean \(\mu_a\). As before, a
learner decides at any time step \(t=1,2,...,\) an arm
\(A_t \in \{1,...,K\}\) for which he observes the independent reward
\(Z_{t} \sim \nu_{A_t}\). The learner aims to find the \(m\) out of
\(K\) arms with the largest expected reward. This set of arm indices is
denoted by \(\mathcal{S}_m^*\). Kaufmann et al. write the in decreasing
order sorted means \((\mu_{1}, ..., \mu_{K})\) as the K-tuple
\((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they require that
\(\mu_{[m]} > \mu_{[m+1]}\) such that the solution \(\mathcal{S}_m^*\)
is unique. The class of bandit problems \(\nu\) for which the latter
condition holds is called \(\mathcal{M}_m\) by Kaufmann et al. At the
end of the sampling procedure, after \(T\) samples (denoted by \(\tau\)
in Kaufmann et al.) the learner is required to return a classification
\(\hat{\mathcal{S}}_m\). This classification is then evaluated by the
loss function
\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
This binary loss is of course very similar to the loss in the
thresholding bandit problem. We can now define a strategy of the learner
as \(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy
defines how he chooses an arm, how many samples are observed, and how
the arms are classified in the end.

When introducing the thresholding bandit setting, we did not mention the
fact that the budget \(T\) does not need to be fixed upfront. Indeed,
the setting in which the budget is \emph{not} fixed upfront might be
more popular among the best arm identification and top-\(m\) literature.
This setting is called \emph{fixed-confidence}, while the setting we
considered so far is called \emph{fixed-budget}. In the fixed-budget
setting, we run algorithms for \(T\) samples and then compare them based
on their expected loss,
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which holds for every
problem \(\nu \in \mathcal{M}_m\) that the classification holds at least
with confidence level \(1-\delta\), that is,
\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
strategy has to achieve this level of confidence in its prediction
before it is allowed to stop sampling. This is the fixed-confidence
case, in which the budget \(T\) is no longer fixed upfront, but becomes
a random variable. We compare algorithms by their expected number of
draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and prefer those which arrive at
the confidence level \(1-\delta\) with a smaller expected budget.

Following Kaufmann et al. (2016), in the fixed confidence setting, a
family of strategies \(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is
called PAC if for every \(\delta\), \(\mathcal{A}(\delta)\) is
\(\delta\)-PAC. On the other hand, in the fixed budget setting, a family
of strategies \(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called
consistent if \(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for
every problem \(\nu \in \mathcal{M}_m\).

Given this setup, we can now follow the arguments of Kaufmann et al.
(2016) to deduce complexity measures for the top-\(m\) problem. As
alluded to earlier, these complexity measures will rely on the
Kullback-Leibler divergence in contrast to the complexity \(H\) used by
Locatelli et al. (2016). Also, when discussing \(H\), we so far
described it as complexity as it measures the difficulty of the problem
by measuring the distance between arms and the threshold. Kaufmann et
al. approach complexity instead from how many samples (what error
probability) one can expect to need in the fixed confidence (fixed
budget) setting. Thus, in order to arrive at their new measure of
complexity, it makes sense to first follow their arguments to a general
lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) in the
case of fixed confidence top-\(m\) problems. This bound is given in
their Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).

@@

Given that we are again in the Top-\(m\) setting, the proof idea is
similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
that we again consider problems where we switch arms around the limit
seperating the two groups of arms as given implicitly by \(\mu_{[m]}\)
and \(\mu_{[m+1]}\). The hope here being that these methods could be
applied to the thresholding bandit problem where the threshold of course
gives the limit between the arms above and below the threshold. As we
have seen in chapter 1, this flip around the threshold was of course
used in the proof of the lower bound in Theorem 1 of Locatelli et al.
(2016). However, there, again, the distributions were assumed to be
Gaussian. This brings the big advantage that the Kullback-Leibler
divergence becomes symmetric, and the feedback can take values on all
\(\mathbb{R}\). And by using the complexity measure \(H(\nu)\), it is
also clear that there exists an arm that is undersampled with respect to
its contribution to the overall complexity of the problem (or sampled
exactly according to its contribution), which leads to a convenient
upper bound on this arms number of draws which is again employed in both
the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in
Locatelli et al. (2016). It is not clear yet, whether the same can also
be done with other complexity measures.

@@

\subsubsection{\texorpdfstring{Likelihood Ratio for Univariate
Exponential Family of Distributions
\label{sec:LRforUnivariateExponentialFamily}}{Likelihood Ratio for Univariate Exponential Family of Distributions }}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}

@@

{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1}
